### 2016-09-06 Documents/bootcamp_syllabus.tex
updated syllabus

Eveything you need, including this document, is posted on
the {\bf course website\/}:
%
\vspace{-0.15in}
\begin{center}
\url{http://databootcamp.nyuecon.com/}
\end{center}
\vspace{-0.15in}
%
The {\bf book\/} has its own site,
% TODO: We need to change this link once gitbook is re-enabled
\vspace{-0.15in}
\begin{center}
\url{https://www.gitbook.com/book/davebackus/test/details}
\end{center}
\vspace{-0.15in}
%
There's a link to it on the course site.
We will not use NYU Classes.

We have set up {\bf announcement and discussion groups\/} (Google groups)
to make announcements and post questions. We will use this to post all assignments and
answer keys.
If you have coding or other questions, we encourage you to post them there.
If you know the answer to someone else's question, we {\bf strongly } encourage you to post that, too.
The links are
% TODO: we need to update these links once we decide where our forum will go
\vspace{-0.1in}
\begin{center}
UG:   \url{https://groups.google.com/forum/#!forum/nyu_data_bootcamp_ug}  \\
MBA:  \url{https://groups.google.com/forum/#!forum/nyu_data_bootcamp_mba}
\end{center}
\vspace{-0.1in}
%
You can access the same links from the course website.  Follow the instructions to join under whatever email address you plan to use.

@@

{\bf Due dates} are posted on the course website.
Assignments, whether code practice or components of the project,
are due at the start of class on the specified dates.
{\bf Dates are not negotiable.
Anything handed in late will get a grade of zero.\/}

@@

{\bf Final grades\/} will be computed from
\begin{center}
\begin{tabular}{ll}
Code Practice (best two of three) & 20\% \\
Exam        & 30\% \\
Project     & 50\% \\
\end{tabular}
\end{center}
Final grades are not subject to any fixed distribution or curve.
The number of A grades, for example,
will depend only on your performance in the course.
If you make a good-faith effort,
we expect it to be hard to get less than a B.
We are the sole judges of what constitutes good-faith effort.

@@

% TODO: we need to fix the email address below once we finish setting up the domain
You can find answers to common questions on the course website.
You can also post questions on the discussion group;
see the link above and on the course website.
For others, email us (\href{mailto:nyu.databootcamp@gmail.com}{nyu.databootcamp@gmail.com}),
the co-teacher, or the teaching fellow; their contact information is on the course website.

@@

On disabilities:
If you have a qualified disability that requires academic accommodation,
please contact the Moses Center for Students with Disabilities
(\href{http://www.nyu.edu/life/safety-health-wellness/students-with-disabilities.html}{CSD},
212-998-4980) and ask them to
send me a letter verifying your registration and outlining the accommodation they recommend.
If you need to take an exam at the CSD,
you must submit a completed Exam Accommodations Form to them
at least one week prior to the scheduled exam time to be assured accommodation.

@@

OLD STUFF

\begin{itemize}
\item Data. We live in a world that's ...
\item Programming. To make sense of the data, you need to be able to code:
to write computer programs to put the data in a form that ...
Be forwarned:  you are expected to write programs in this course.
This can be incredibly frustrating and requires enormous patience.
If that's not your thing, you should not take this course.
\item Graphics.
\end{itemize}

>>>>

Eveything you need, including this document, is posted on
the {\bf course website\/}:
%
\vspace{-0.15in}
\begin{center}
\url{http://databootcamp.nyuecon.com/}
\end{center}
\vspace{-0.15in}
%
The {\bf book\/} has its own site,
\vspace{-0.15in}
\begin{center}
\url{https://www.gitbook.com/book/nyudatabootcamp/data-bootcamp/details}
\end{center}
\vspace{-0.15in}
%
There's a link to it on the course site.
We will not use NYU Classes.

We have set up {\bf announcement and discussion groups\/} (Google groups)
to make announcements and post questions. We will use this to post all assignments and
answer keys.
If you have coding or other questions, we encourage you to post them there.
If you know the answer to someone else's question, we {\bf strongly } encourage you to post that, too.
The links are
\vspace{-0.1in}
\begin{center}
UG:   \url{https://groups.google.com/forum/#!forum/nyu_data_bootcamp_ug}  \\
MBA:  \url{https://groups.google.com/forum/#!forum/nyu_data_bootcamp_mba}
\end{center}
\vspace{-0.1in}
%
You can access the same links from the course website.  Follow the instructions to join under whatever email address you plan to use.

@@

{\bf Due dates} are posted on the course website.
Assignments, whether code practice or components of the project,
are due at the start of class on the specified dates.

{\bf Dates are not negotiable.
Anything handed in late will get a grade of zero.\/}

@@

{\bf Final grades\/} will be computed from
\begin{center}
\begin{tabular}{ll}
Code Practice (best two of three) & 20\% \\
Exam        & 30\% \\
Project     & 50\% \\
\end{tabular}
\end{center}

Final grades are not subject to any fixed distribution or curve.
The number of A grades, for example,
will depend only on your performance in the course.
If you make a good-faith effort,
we expect it to be hard to get less than a B.
We are the sole judges of what constitutes good-faith effort.

@@

You can find answers to common questions on the course website.
You can also post questions on the discussion group;
see the link above and on the course website.
For others, email us (\href{mailto:nyu.databootcamp@gmail.com}{nyu.databootcamp@gmail.com}),
the co-teacher, or the teaching fellow; their contact information is on the course website.

@@

On disabilities:
If you have a qualified disability that requires academic accommodation,
please contact the Moses Center for Students with Disabilities
(\href{http://www.nyu.edu/life/safety-health-wellness/students-with-disabilities.html}{CSD},
212-998-4980) and ask them to
send us a letter verifying your registration and outlining the accommodation they recommend.
If you need to take an exam at the CSD,
you must submit a completed Exam Accommodations Form to them
at least one week prior to the scheduled exam time to be assured accommodation.

@@
